How to be a good member of a scientific software community [Article v\versionnumber]

### 2021-08-30 paper.tex
Dave's suggestions

Along the same lines, it is often valuable to construct a fake or minimal data
set where the correct answer is known (or easily computed outside the program).
This is particularly important when your concern is for the program's
correctness. This is particularly important when your concern is that the
program is producing incorrect answers due to a coding error or assumptions
incompatible with the input data.

@@

As the user and developer community grows, other people will get involved in
supporting users. It's still your obligation as a developer to maintain those
standards.  Making sure that racist, sexist, anti-LGBTQ, etc language and
behavior is unwelcome and unacceptable is simply the moral thing to do (it's
also pragmatic --- can you really afford to lose talented developers and users
because they don't feel welcome?) This doesn't just mean use of epithets in
messages (though that's clearly unacceptable). Keep an eye on how things are
named, on jokes present in the code or messages, on whose opinions are listened
to and who is ignored.  Above all, if someone tells you a particular behavior or
situation is harmful, \emph{believe them}.  Something that feels minor (or is
just a joke) to you may hit others very differently, and part of respect is
understanding and accounting for that.

@@

\section{Other Contributions}
%%%%%%%%%%%%%%%
% You should include all people who have filed issues that were
% accepted into the paper, or that upon discussion altered what was in the paper.
% Multiple significant contributions might mean that the contributor
% should be moved to authorship at the discretion of the a
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io for
% more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%
Dr. Tod D. Romo reviewed the document for style and content. Dr. Justin Lemkul
made numerous helpful suggestions, particularly regarding language
accessibility.

>>>>

Along the same lines, it is often valuable to construct a fake or minimal data
set where the correct answer is known (or easily computed outside the program).
This is particularly important when your concern is that the program is
producing incorrect answers due to a coding error or assumptions incompatible
with the input data. The more you precisely you can narrow down what's going
wrong, the easier the problem will be to diagnose.

@@

As the user and developer community grows, other people will get involved in
supporting users. It's still your obligation as a developer to maintain those
standards.  Making sure that racist, sexist, anti-LGBTQ, etc language and
behavior is unwelcome and unacceptable is simply the moral thing to do.  This
doesn't just mean use of epithets in messages (though that's clearly
unacceptable). Keep an eye on how things are named, on jokes present in the code
or messages, on whose opinions are listened to and who is ignored.  Above all,
if someone tells you a particular behavior or situation is harmful,
\emph{believe them}.  Something that feels minor (or is just a joke) to you may
hit others very differently, and part of respect is understanding and accounting
for that.

@@

\section{Other Contributions}
%%%%%%%%%%%%%%%
% You should include all people who have filed issues that were
% accepted into the paper, or that upon discussion altered what was in the paper.
% Multiple significant contributions might mean that the contributor
% should be moved to authorship at the discretion of the a
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io for
% more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%
Dr. Tod D. Romo reviewed the document for style and content. Dr. Justin A.
Lemkul made numerous helpful suggestions, particularly regarding language
accessibility. Dr. David H. Mathews provided several editorial suggestions.
